---
title: IMDB Movie Explorer 
subtitle: Exploratory Analysis of Movie Database
author: Zvonko Kosic
#output: ioslides_presentation
output: github_document
mode: selfcontained
---
 
 
## Why? Exploratory Analysis App

- Summarize main characeteristics
- Seeing what the data can tell us
- Recognize patterns in advance
- e.g glampse of how ratings are distributed over genre
```{r echo=FALSE}
require("ggplot2")
require("ggplot2movies")
library("gridExtra")

mm <- ggplot2movies::movies

mm$Genre <- ifelse(mm$Action == 1,"Action",
                        ifelse(mm$Animation == 1,"Animation",
                               ifelse(mm$Comedy == 1,"Comedy",
                                      ifelse(mm$Drama == 1,"Drama",
                                             ifelse(mm$Documentary == 1,"Documentary",
                                                    ifelse(mm$Romance == 1,"Romance",
                                                           ifelse(mm$Short == 1,"Short","none")))))))

mm <- subset(mm, select=-c(Action,Animation,Comedy,Drama,Documentary,Romance,Short))

mm$length.bin <- cut(mm$length, c(0,100,200,300,400,500,600,6000))


p0 <- ggplot(mm,aes(x=Genre,y=rating)) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) 
p0 <- p0 + geom_boxplot(aes(fill=Genre)) + ggtitle("Rating per Genre") + xlab("Genre") + ylab("IMDB Rating")

p1 <- ggplot(mm, aes(x=year, y=rating))
p1 <- p1 + geom_point(aes(color=Genre,size=budget)) + ggtitle("Rating per Genre") + xlab("Year") + ylab("IMDB Rating")
```
```{r echo=FALSE, fig.height=4}
p0
```

--- 
 
## What? Exploratory Analysis App
- Mainly visualizations of various variables
- Scatter and bar plots
- Grid of several variables compared to others

```{r echo=FALSE, fig.height=4, fig.width=12}
grid.arrange(p0, p1,ncol=2)
```

--- 

## ShinyApp! Exploratory Analysis App
- IMDB Movies Database Explorer
- Visualize the potential dependancy between
  several variables
- Limit every variable to specific intervalls
- Grid plot with a lot of dependent variables
  at once


--- 

## Conclusion. Exploratory Analysis App
- John W. Tukey said that too much emphasis was placed
on statistical hypothesis testing; more emphasis is/was
needed on eploratory analysis
- Before conducting any regression, prediction exploratory
analysis is the first step
- This app can help greatly to understand the underlying
data.
- Could be expanded to automatically extracts the variables
and builds the ui on demand
--- 

 
 
